\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

In this section, we present current languages for RDF constraint formulation and RDF data validation\footnote{
\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
\emph{SPIN}: \url{http://spinrdf.org},
\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
\emph{Bibframe}: \url{http://bibframe.org},
\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
%\emph{Schematron}: \url{http://www.schematron.com},
%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
}.
SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.

@@

The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles. It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax. Its primary purpose is to specify the components used in Dublin Core metadata. Nilsson et al. \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model. A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile. DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to. The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with DSP.

\emph{RDF Schemarama} 
is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
It allows to check that RDF data has required properties and
it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
%
%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
%
%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.

In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.

>>>>

In this section, we present current languages for RDF constraint formulation and RDF data validation\footnote{
\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
\emph{SPIN}: \url{http://spinrdf.org},
\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
\emph{Bibframe}: \url{http://bibframe.org},
\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
\emph{RDF Schemarama}: \url{http://www.xml.com/pub/a/2001/02/07/schemarama.html}
%\emph{Schematron}: \url{http://www.schematron.com},
%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
}.
SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.

@@

The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles. It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax. Its primary purpose is to specify the components used in Dublin Core metadata. Nilsson et al. \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model. A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile. DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to. \emph{BIBFRAME} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP. \emph{BIBFRAME Profiles} \cite{DCMI-Bibframe-Profiles-2014} are essentially identical to DCAPs.

\emph{Schemarama} is a validation technique for specifying the types of sub-graphs you want to have connected to a particular set of nodes in an RDF Graph. Schemarama allows to check that RDF data has required properties. Schemarama is based on Schematron \cite{ISO/IEC-2006}, an XML schema and XML structure validation language which works by finding tree patterns within an XML document. Schemarama is also based on the \emph{Squish RDF Query language} \cite{Miller-2001}, an SQL-like query language for RDF, instead of SPARQL.

%
%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
%
%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.

In addition to the formulation of constraints, SPIN (open source API), Stardog ICV (as part of the Stardog RDF database), DQTP (tests), Pellet ICV (extension of Pellet OWL 2 DL reasoner) and ShEx offer executable validation systems using SPARQL as implementation language.
